---
title: "Exploratory Analysis of Model Outputs"
author: "Yimeng Yin"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output: 
  html_document:
    toc: true
    toc_depth: 4
---

```{r runall, eval=FALSE, echo=FALSE}
# When we want a final report, run the following code selectively "by hand" (interactively) -- NEVER using Knit with eval=TRUE

folder_run <- "IO_Initial_Runs_3"  # must be the same one as in chunk "Read" below

rmdfn <- "Analysis_Outputs.rmd" # this file
outfn <- paste0(folder_run,"/Analysis_Outputs.html")

rmarkdown::render(rmdfn, output_format="html_document", output_file=outfn)

# Note that it is safest to fully exit RStudio and restart it before running the whole thing. Otherwise knitr can get confused
# and include repetitive information in the output html file.

```

```{r mainSet options, echo=FALSE, cache=FALSE}

options(width=120)
knitr::opts_chunk$set(fig.width=14, fig.height=5, echo=FALSE)
# Note: when saving maps (ggsave), width=16, height=9 seems to get rid of white space

```




```{r Preamble, echo = FALSE, include  = FALSE}
library(reshape2)
library(plyr)
library(dplyr)
library(tidyr)
library(ggplot2)
library(knitr)

rm(list = ls())
source("Functions.R")

```


```{r Read, echo=FALSE, include = FALSE}
## Combine selected files into a single list.

folder_run <- "IO_Initial_Runs_3"
file_select <- dir(folder_run, pattern = "06-13")


fn <- function(x) {
       load(paste0(folder_run, "/", x))
       outputs_list
  }

lists_all        <- alply(file_select, 1, fn)
names(lists_all) <- laply(lists_all, function(x) x$paramlist$runname)

## Combine the results into a single data frame.
results_all <- ldply(lists_all, function(x) x$results) %>% select(-X1)

lists_all$R4F2$paramlist$plan_contributions

```


```{r, include = FALSE, eval= FALSE}

# select variables to be displayed in the kable function. See below for a list of all avaiable variables and explanations.
var.display <- c("year",  "AL",    "MA",    "AA",   "FR", "FR_MA",
                 # "ExF",   
                 "UAAL",  "EUAAL", "LG",    "NC",    "SC",    
                 "ADC", "EEC", "ERC",  "C", "B",     
                 # "I.r" ,   "I.e", 
                 "i",    "i.r",
                 "ADC_PR", "C_PR", "ERC_PR", "PR"# , "dERC_PR"
                 # "AM", "PR",
                 # "C_ADC"
                 )

r1 <- results_all %>% filter(sim %in% 1, runname == "R4F3") %>% select(one_of(var.display)) %>% 
  mutate(PR_growth = 100 * (PR/lag(PR) - 1) )
kable(r1, digits = 2)

r1$PR_growth



```


```{r Draw_function, echo = FALSE, include = FALSE}

get_quantiles <- function( runName,     # character
                           varName,     # character
                           data = results_all,
                           year.max = 100,
                           qts = c(0.1, 0.25, 0.5, 0.75, 0.9)){
  
#   runName = c("R4F1")     # character
#   varName = "FR"     # character
#   data = results_all
#   year.max = 100
#   qts = c(0.1, 0.25, 0.5, 0.75, 0.9)
#   
  
  df <- data %>% filter(runname %in% runName) %>%  
        select_("runname",  "sim","year", varName) %>% spread_("year", varName)
  
  fn <- function(df) { 
    df_q <- sapply(select(df, -sim, -runname), function(x) quantile(x, qts)) %>% as.data.frame
    
    df_q %<>% mutate(Quantile = rownames(df_q)) %>% gather(year, Value, -Quantile) %>%
    
    mutate(year = f2n(year),
           Quantile = factor(Quantile)) %>% filter(year <= year.max)
    
    df_q %<>% spread(Quantile, Value)
    }
  
  df <- ldply(split(df, df$runname), fn, .id = "runname")

  return(df)
  
}

draw_quantiles  <- function(runName,     # character
                            varName,     # character
                            data = results_all,
                            year.max = 80,
                            qts = c(0.1, 0.25, 0.5, 0.75, 0.9),
                            ylim = NULL){
 
  df_q <- get_quantiles(runName = runName, 
                        varName = varName,
                        data    = data,
                        year.max = year.max,
                        qts = qts)  %>% 
          gather(Quantile, Value, -runname, -year)
 
  plot_q <- 
    ggplot(df_q, aes(x = year, y = Value, color = Quantile)) + theme_bw() + 
    geom_point(size = 1.5) + geom_line()+ 
    labs(y = varName, title = paste0("Quantile plot of ", varName, " in ", runName))
  
  if(length(runName) > 1) plot_q <- plot_q + facet_grid(. ~ runname) 
  if(!is.null(ylim)) plot_q <- plot_q + coord_cartesian(ylim = ylim)
  
  plot_q
}


# get_quantiles(c("R4F1", "R4F2"), "ERC_PR")
# draw_quantiles(c("R4F1", "R4F2"), "ERC_PR", ylim = c(-0.5, 20))

```



# Variables to Examine
- **FR:** Funded ratio
- **ERC_PR:** Employer contribution rates
- **C_PR:** Total contribution rates
- **B_PR:** Benefit payment rates 


# Funding Policies:
**F1:** Highly smoothed

- asset smoothing: 10 years;
- amortization: constant percent, 30 years, open


**F2:** highly unsmoothed

- market assets;
- amortization: constant dollar, 10 years, closed


**F3:** typical

- asset smoothing: 5 years;
- amortization constant percent, 20 years, open



# Notes

Using rp2000.hybrid


# Scenario 1 
Fixed Return Fixed discount rate and investment return, 7.5% each




```{r S1, echo = FALSE, cache = F , eval = TRUE}

prefix <- "R1F"

draw_quantiles(paste0(prefix, 1:3), "FR", ylim = c(40, 120)) %>% print

draw_quantiles(paste0(prefix, 1:3), "ERC_PR", ylim = c(-2, 100)) %>% print

draw_quantiles(paste0(prefix, 1:3), "C_PR", ylim = c(-2, 100)) %>% print

draw_quantiles(paste0(prefix, 1:3), "B_PR") %>% print


```


# Scenario 2 
Fixed discount rate 7.5%, fixed investment return 5.5%

```{r S2, echo = FALSE, cache = F, eval = FALSE}

prefix <- "R2F"

draw_quantiles(paste0(prefix, 1:3), "FR", ylim = c(0, 120))

draw_quantiles(paste0(prefix, 1:3), "ERC_PR")

draw_quantiles(paste0(prefix, 1:3), "C_PR")

draw_quantiles(paste0(prefix, 1:3), "B_PR")

```


# Scenario 3 
Fixed discount rate 7.5%, fixed investment return  9.5%


```{r S3, echo = FALSE, cache = F, eval = FALSE}

prefix <- "R3F"

draw_quantiles(paste0(prefix, 1:3), "FR", ylim = c(60, 350))

draw_quantiles(paste0(prefix, 1:3), "ERC_PR")

draw_quantiles(paste0(prefix, 1:3), "C_PR")

draw_quantiles(paste0(prefix, 1:3), "B_PR")

```


# Scenario 4 
Fixed discount rate 7.5%, stochastic investment return arithmetic mean 7.5%, sd 12%


```{r S4, echo = FALSE, cache = F}

prefix <- "R4F"

draw_quantiles(paste0(prefix, 1:3), "FR", ylim = c(-5, 250)) %>% print

draw_quantiles(paste0(prefix, 1:3), "ERC_PR", ylim = c(-2, 30)) %>% print

draw_quantiles(paste0(prefix, 1:3), "C_PR", ylim = c(-2, 30)) %>% print

draw_quantiles(paste0(prefix, 1:3), "B_PR") %>% print

```


# Scenario 5 
Fixed Return Fixed discount rate and investment return, 7.5% each, with 5-year period of low returns


```{r S5, echo = FALSE, cache = F, eval = FALSE}

prefix <- "R5F"

draw_quantiles(paste0(prefix, 1:3), "FR", ylim = c(40, 120))

draw_quantiles(paste0(prefix, 1:3), "ERC_PR")

draw_quantiles(paste0(prefix, 1:3), "C_PR")

draw_quantiles(paste0(prefix, 1:3), "B_PR")

```



# Scenario 6 
Fixed Return Fixed discount rate and investment return, 7.5% each, with a 5-year period of low employer contributions


```{r S6, echo = FALSE, cache = F, eval = FALSE}

prefix <- "R6F"

draw_quantiles(paste0(prefix, 1:3), "FR", ylim = c(40, 120))

draw_quantiles(paste0(prefix, 1:3), "ERC_PR")

draw_quantiles(paste0(prefix, 1:3), "C_PR")

draw_quantiles(paste0(prefix, 1:3), "B_PR")

```



# Look at the Geometric returns in Scenario 4


```{r geoReturn, echo = FALSE}

get_geoReturn <- function(x) prod(1 + x)^(1/length(x)) - 1

df <- results_all %>% filter(runname == "R4F1") %>%  group_by(sim) %>% 
      summarise(geoReturn = get_geoReturn(i.r))

df$geoReturn %>% summary
df$geoReturn %>% hist(40, FALSE,  main = "Histogram of Geometric Returns")
abline(v = 0.075, col = "red")


```




```{r move_file, eval= FALSE}



```




