---
title: "Exploratory Analysis of Model Outputs"
author: "Yimeng Yin"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output: 
  html_document:
    toc: true
    toc_depth: 4
---


```{r mainSet options, echo=FALSE, cache=FALSE}

# options(width=120)
# knitr::opts_chunk$set(fig.width=14, fig.height=5, echo=FALSE)
# # Note: when saving maps (ggsave), width=16, height=9 seems to get rid of white space

```




```{r Preamble, echo = FALSE, include  = FALSE}
library(reshape2)
library(plyr)
library(dplyr)
library(tidyr)
library(ggplot2)
library(knitr)
library(magrittr) # to use %<>%

rm(list = ls())

run_knitr <- FALSE

if(run_knitr) source("../Functions.R") else source("Functions.R")


```


```{r Read, echo=FALSE, include = FALSE}
## Combine selected files into a single list.

if(run_knitr) folder_run <- "../IO_ActMethods" else folder_run <- "IO_ActMethods"

file_select <- dir(folder_run, pattern = ".RData")

fn <- function(x) {
       load(paste0(folder_run, "/", x))
       outputs_list
  }

lists_all        <- alply(file_select, 1, fn)
names(lists_all) <- laply(lists_all, function(x) x$paramlist$runname)

## Combine the results into a single data frame.
results_all <- ldply(lists_all, function(x) x$results) %>% select(-X1)


```



```{r, include = FALSE, eval= FALSE}

# select variables to be displayed in the kable function. See below for a list of all avaiable variables and explanations.
var.display <- c("runname", "year",  "AL",    "MA",    "AA",   "FR", "FR_MA",
                 # "ExF",   
                 "UAAL",  "EUAAL", "LG",    "NC",    "SC",    
                 "ADC", "EEC", "ERC",  "C", "B",     
                 # "I.r" ,   "I.e", 
                 "i",    "i.r",
                 "ADC_PR", "C_PR", "ERC_PR", "PR"# , "dERC_PR"
                 # "AM", "PR",
                 # "C_ADC"
                 )

r1 <- results_all %>% filter(sim %in% 1, year == 1) %>% select(one_of(var.display)) %>% 
      mutate(PR_growth = 100 * (PR/lag(PR) - 1) )
kable(r1, digits = 2)

# Under 


```





# Variables to Examine
- **FR:** Funded ratio
- **ERC_PR:** Employer contribution rates
- **C_PR:** Total contribution rates
- **B_PR:** Benefit payment rates 


# Funding Policies:
**F1:** Highly smoothed

- asset smoothing: 10 years;
- amortization: constant percent, 30 years, open


**F2:** highly unsmoothed

- market assets;
- amortization: constant dollar, 10 years, closed


**F3:** typical

- asset smoothing: 5 years;
- amortization constant percent, 20 years, open



# Notes

Using rp2000.hybrid


# Scenario 1 
Fixed Return Fixed discount rate and investment return, 7.5% each




```{r S1, echo = FALSE, cache = F , eval = TRUE}

prefix <- "R1F"

draw_quantiles(paste0(prefix, 1:3), "FR", ylim = c(40, 120)) %>% print

draw_quantiles(paste0(prefix, 1:3), "ERC_PR", ylim = c(-2, 100)) %>% print

draw_quantiles(paste0(prefix, 1:3), "C_PR", ylim = c(-2, 100)) %>% print

draw_quantiles(paste0(prefix, 1:3), "B_PR") %>% print


```




