---
title: "Exploratory Analysis of Model Outputs"
author: "Yimeng Yin"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output: 
  html_document:
    toc: true
    toc_depth: 4
---


```{r mainSet_options, echo=FALSE, cache=FALSE}

# options(width=140)
# knitr::opts_chunk$set(fig.width=16, fig.height=5, echo=FALSE)
# # Note: when saving maps (ggsave), width=16, height=9 seems to get rid of white space

```




```{r Preamble, echo = FALSE, include  = FALSE}
library(reshape2)
library(plyr)
library(dplyr)
library(tidyr)
library(ggplot2)
library(knitr)
library(magrittr) # to use %<>%
library(zoo)
library(grid)

rm(list = ls())

run_knitr <- F
# When knitting HTML files, the working directory will be changed to the on where the .rmd file is located.
# The relative paths must be modified if they are not relative to the folder the .rmd file is located. 
# (When running the code line by line, it is covenient to set the paths relative to the folder of main model.)

if(run_knitr) source("../Functions.R") else source("Functions.R")

```


```{r Read, echo=FALSE, include = FALSE}
## Combine selected files into a single list.

IO_folder <- "IO_M2.1_new"

if(run_knitr) IO_folder <- paste0("../", IO_folder)

get_results <- function(IO_folder){
  
  fn <- function(x) {
    load(paste0(IO_folder, "/", x))
    outputs_list$results}

  file_select <- dir(IO_folder, pattern = "^Outputs")
  results_all <- adply(file_select, 1, fn) %>% select(-X1)
}

results_all <- get_results(IO_folder)
```


```{r, echo=FALSE, include = FALSE}

var.display <- c( "runname", "year",
                 "FR","AL","AA","MA",
                 # "AL_PR", "AL.act_PR", "AL.ret_PR","AL.term_PR", 
                 "NC_PR", "NC.act_PR", "NC.term_PR", 
                 "SC_PR", "C_PR", "ERC_PR",
                 "MA_PR",   
                 "PR.growth", 
                 "ExF_PR",
                 "AL", "C","B","PR",
                 "ExF"
)

results_all %>% filter(runname == "D1F075-average_g1", year %in% 1:10, sim == 1) %>% select(one_of(var.display))

```



# Demographics: Average Plan
```{r, echo = FALSE, cache = F , eval = TRUE, fig.width=20, fig.height=8}

prefix <- "D1F075-"
runs_M2.1_avg <- c(
  "average_gn2",
  "average_gn1",
  "average",
  "average_g1",
  "average_g2"
)
draw_quantiles(c(paste0(prefix, runs_M2.1_avg)), "FR_MA", ylim = c(-10, 400), year.max = 60)$plot %>% print
draw_quantiles(c(paste0(prefix, runs_M2.1_avg)), "C_PR", ylim = c(-2, 35),  year.max = 40)$plot %>% print
#draw_quantiles(c(paste0(prefix, runs_M2.1_avg)), "ERC_PR", ylim = c(-2, 35),year.max = 40)$plot %>% print
draw_quantiles(c(paste0(prefix, runs_M2.1_avg)), "MA_PR", ylim = c(-10, 2000), year.max = 40)$plot %>% print

```



# Demographics: Mature Plan
```{r, echo = FALSE, cache = F , eval = TRUE, fig.width=20, fig.height=8}

prefix <- "D1F075-"

runs_M2.1_mature <- c(
 "mature1",
 "mature1_gn1",
 "mature2",
 "mature2_gn1")
 
draw_quantiles(c(paste0(prefix, runs_M2.1_mature)), "FR_MA", year.max = 40)$plot %>% print
draw_quantiles(c(paste0(prefix, runs_M2.1_mature)), "C_PR", ylim = c(-2, 35),  year.max = 40)$plot %>% print
# draw_quantiles(c(paste0(prefix, runs_M2.1_mature)), "ERC_PR", ylim = c(-2, 35),year.max = 40)$plot %>% print
draw_quantiles(c(paste0(prefix, runs_M2.1_mature)), "MA_PR", ylim = c(-10, 2000), year.max = 40)$plot %>% print


```


# Demographics: Immature Plan
```{r, echo = FALSE, cache = F , eval = TRUE, fig.width=20, fig.height=10}
prefix <- "D1F075-"
runs_M2.1_immature <- c( "immature", "immature_g1")

draw_quantiles(c(paste0(prefix, runs_M2.1_immature)), "FR_MA", year.max = 40)$plot %>% print
draw_quantiles(c(paste0(prefix, runs_M2.1_immature)), "C_PR", ylim = c(-2, 35),  year.max = 40)$plot %>% print
# draw_quantiles(c(paste0(prefix, runs_M2.1_immature)), "ERC_PR", ylim = c(-2, 35),year.max = 40)$plot %>% print
draw_quantiles(c(paste0(prefix, runs_M2.1_immature)), "MA_PR", ylim = c(-10, 2000), year.max = 40)$plot %>% print
```



# Investment returns: Fixed ir.mean with various sd

```{r, echo = FALSE, cache = F , eval = TRUE, fig.width=20, fig.height=4}

prefix1 <- "I1F075-"
runs_M2.1_I1 <- 1:5


draw_quantiles(c(paste0(prefix1, runs_M2.1_I1)), "FR_MA", year.max = 40)$plot %>% print
draw_quantiles(c(paste0(prefix1, runs_M2.1_I1)), "C_PR", ylim = c(-2, 35),  year.max = 40)$plot %>% print
# draw_quantiles(c(paste0(prefix1, runs_M2.1_I1)), "ERC_PR", ylim = c(-2, 35),year.max = 40)$plot %>% print
draw_quantiles(c(paste0(prefix1, runs_M2.1_I1)), "MA_PR", year.max = 40)$plot %>% print

```

# Investment returns: Constant Sharpe Ratio
High standard deviations (risks) are associated with high returns.

```{r, echo = FALSE, cache = F , eval = TRUE, fig.width=20, fig.height=4}
prefix2 <- "I2F075-"
runs_M2.1_I2 <- 1:5

draw_quantiles(c(paste0(prefix2, runs_M2.1_I2)), "FR_MA", year.max = 40)$plot %>% print
draw_quantiles(c(paste0(prefix2, runs_M2.1_I2)), "C_PR", ylim = c(-2, 35),  year.max = 40)$plot %>% print
draw_quantiles(c(paste0(prefix2, runs_M2.1_I2)), "ERC_PR", ylim = c(-2, 35),year.max = 40)$plot %>% print
draw_quantiles(c(paste0(prefix2, runs_M2.1_I2)), "MA_PR", year.max = 40)$plot %>% print


```

# Investment returns: Constant Sharpe Ratio, DC equal to implied geom mean
High standard deviations (risks) are associated with high returns.
DC is set to ir.mean - ir.sd^2/2.
All plans start with the same asset value.

```{r, echo = FALSE, cache = F , eval = TRUE, fig.width=20, fig.height=4}

prefix3 <- "I3F075-"
runs_M2.1_I3 <- 1:5

# using implied geometric mean as discoun rate. Initial MA adjusted accordingly. 
draw_quantiles(c(paste0(prefix3, runs_M2.1_I3)), "FR_MA", year.max = 40)$plot %>% print
draw_quantiles(c(paste0(prefix3, runs_M2.1_I3)), "C_PR", ylim = c(-2, 35),  year.max = 40)$plot %>% print
draw_quantiles(c(paste0(prefix3, runs_M2.1_I3)), "ERC_PR", ylim = c(-2, 35),year.max = 40)$plot %>% print
draw_quantiles(c(paste0(prefix3, runs_M2.1_I3)), "MA_PR", year.max = 40)$plot %>% print
```


# Benefit:
1: No COLA; 2: 2% COLA

```{r, echo = FALSE, cache = F , eval = TRUE, fig.width=20, fig.height=10}

prefix <- "BF075-"
runs_M2.1_B <- 1:2

draw_quantiles(c(paste0(prefix, runs_M2.1_B)), "FR_MA", year.max = 40)$plot %>% print
draw_quantiles(c(paste0(prefix, runs_M2.1_B)), "C_PR", ylim = c(-2, 35),  year.max = 40)$plot %>% print
# draw_quantiles(c(paste0(prefix, runs_M2.1_B)), "ERC_PR", ylim = c(-2, 35),year.max = 40)$plot %>% print
draw_quantiles(c(paste0(prefix, runs_M2.1_B)), "MA_PR", year.max = 40)$plot %>% print
```




