---
title: "Exploratory Analysis of Model Outputs"
author: "Yimeng Yin"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output: 
  html_document:
    toc: true
    toc_depth: 4
---


```{r mainSet options, echo=FALSE, cache=FALSE}

options(width=120)
knitr::opts_chunk$set(fig.width=14, fig.height=5, echo=FALSE)
# Note: when saving maps (ggsave), width=16, height=9 seems to get rid of white space

```




```{r Preamble, echo = FALSE, include  = FALSE}
library(reshape2)
library(plyr)
library(dplyr)
library(tidyr)
library(ggplot2)
library(knitr)
library(magrittr) # to use %<>%

rm(list = ls())
source("../Functions.R")

```


```{r Read, echo=FALSE, include = FALSE}
## Combine selected files into a single list.

folder_run <- "../IO_Initial_Runs_2"
file_select <- dir(folder_run, pattern = ".RData")


fn <- function(x) {
       load(paste0(folder_run, "/", x))
       outputs_list
  }

lists_all        <- alply(file_select, 1, fn)
names(lists_all) <- laply(lists_all, function(x) x$paramlist$runname)

## Combine the results into a single data frame.
results_all <- ldply(lists_all, function(x) x$results) %>% select(-X1)


```


```{r, echo = FALSE}

# select variables to be displayed in the kable function. See below for a list of all avaiable variables and explanations.

var.display <- c("runname", "year",  "AL",    "AA",   "FR", "NC",    "SC", "UAAL",
                "AL_PR", "NC_PR", "C_PR", "ERC_PR", "PR")

r1 <- results_all %>% filter(sim %in% 1, year == 1) %>% select(one_of(var.display))
kable(r1, digits = 2)

r1$PR_growth

```



# Variables to Examine
- **FR:** Funded ratio
- **ERC_PR:** Employer contribution rates
- **C_PR:** Total contribution rates
- **B_PR:** Benefit payment rates 


# Funding Policies:
**F1:** Highly smoothed

- asset smoothing: 10 years;
- amortization: constant percent, 30 years, open


**F2:** highly unsmoothed

- market assets;
- amortization: constant dollar, 10 years, closed


**F3:** typical

- asset smoothing: 5 years;
- amortization constant percent, 20 years, open



# Notes

Using rp2000.hybrid


# Scenario 1 
Fixed Return Fixed discount rate and investment return, 7.5% each




```{r S1, echo = FALSE, cache = F , eval = TRUE}

prefix <- "R1F"

draw_quantiles(paste0(prefix, 1:3), "FR", ylim = c(40, 120)) %>% print

draw_quantiles(paste0(prefix, 1:3), "ERC_PR", ylim = c(-2, 30)) %>% print

draw_quantiles(paste0(prefix, 1:3), "C_PR", ylim = c(-2, 30)) %>% print

draw_quantiles(paste0(prefix, 1:3), "B_PR") %>% print


```


# Scenario 2 
Fixed discount rate 7.5%, fixed investment return 5.5%

```{r S2, echo = FALSE, cache = F, eval = T}

prefix <- "R2F"

draw_quantiles(paste0(prefix, 1:3), "FR", ylim = c(0, 120))

draw_quantiles(paste0(prefix, 1:3), "ERC_PR")

draw_quantiles(paste0(prefix, 1:3), "C_PR")

draw_quantiles(paste0(prefix, 1:3), "B_PR")

```


# Scenario 3 
Fixed discount rate 7.5%, fixed investment return  9.5%


```{r S3, echo = FALSE, cache = F, eval = T}

prefix <- "R3F"

draw_quantiles(paste0(prefix, 1:3), "FR", ylim = c(60, 350))

draw_quantiles(paste0(prefix, 1:3), "ERC_PR")

draw_quantiles(paste0(prefix, 1:3), "C_PR")

draw_quantiles(paste0(prefix, 1:3), "B_PR")

```


# Scenario 4 
Fixed discount rate 7.5%, stochastic investment return arithmetic mean 7.5%, sd 12%


```{r S4, echo = FALSE, cache = F}

prefix <- "R4F"

draw_quantiles(paste0(prefix, 1:3), "FR", ylim = c(-5, 250)) %>% print

draw_quantiles(paste0(prefix, 1:3), "ERC_PR", ylim = c(-2, 30)) %>% print

draw_quantiles(paste0(prefix, 1:3), "C_PR", ylim = c(-2, 30)) %>% print

draw_quantiles(paste0(prefix, 1:3), "B_PR") %>% print

```


# Scenario 5 
Fixed Return Fixed discount rate and investment return, 7.5% each, with 5-year period of low returns


```{r S5, echo = FALSE, cache = F, eval = T}

prefix <- "R5F"

draw_quantiles(paste0(prefix, 1:3), "FR", ylim = c(40, 120))

draw_quantiles(paste0(prefix, 1:3), "ERC_PR")

draw_quantiles(paste0(prefix, 1:3), "C_PR")

draw_quantiles(paste0(prefix, 1:3), "B_PR")

```



# Scenario 6 
Fixed Return Fixed discount rate and investment return, 7.5% each, with a 5-year period of low employer contributions


```{r S6, echo = FALSE, cache = F, eval = T}

prefix <- "R6F"

draw_quantiles(paste0(prefix, 1:3), "FR", ylim = c(40, 120))

draw_quantiles(paste0(prefix, 1:3), "ERC_PR")

draw_quantiles(paste0(prefix, 1:3), "C_PR")

draw_quantiles(paste0(prefix, 1:3), "B_PR")

```



# Look at the Geometric returns in Scenario 4


```{r geoReturn, echo = FALSE}

get_geoReturn <- function(x) prod(1 + x)^(1/length(x)) - 1

df <- results_all %>% filter(runname == "R4F1") %>%  group_by(sim) %>% 
      summarise(geoReturn = get_geoReturn(i.r))

df$geoReturn %>% summary
df$geoReturn %>% hist(40, FALSE,  main = "Histogram of Geometric Returns")
abline(v = 0.075, col = "red")


```




```{r move_file, eval= FALSE}



```




