---
title: "Exploratory Analysis of Model Outputs"
author: "Yimeng Yin"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output: 
  html_document:
    toc: true
    toc_depth: 4
---


```{r mainSet options, echo=FALSE, cache=FALSE}

# options(width=140)
# knitr::opts_chunk$set(fig.width=16, fig.height=5, echo=FALSE)
# # Note: when saving maps (ggsave), width=16, height=9 seems to get rid of white space

```




```{r Preamble, echo = FALSE, include  = FALSE}
library(reshape2)
library(plyr)
library(dplyr)
library(tidyr)
library(ggplot2)
library(knitr)
library(magrittr) # to use %<>%
library(zoo)
library(grid)

rm(list = ls())

run_knitr <- F

if(run_knitr) source("../Functions.R") else source("Functions.R")

```


```{r Read, echo=FALSE, include = FALSE}
## Combine selected files into a single list.

if(run_knitr) folder_run <- "../IO_M1" else folder_run <- "IO_M1"

file_select <- dir(folder_run, pattern = ".RData")

fn <- function(x) {
       load(paste0(folder_run, "/", x))
       outputs_list
  }

lists_all        <- alply(file_select, 1, fn)
names(lists_all) <- laply(lists_all, function(x) x$paramlist$runname)

## Combine the results into a single data frame.
results_all <- ldply(lists_all, function(x) x$results) %>% select(-X1)

rm(lists_all)
```


```{r Read, echo=FALSE, include = FALSE}

results_all %<>% group_by(runname, sim) %>% 
                 mutate(dFR = FR - lag(FR),
                        dFR_MA = FR_MA - lag(FR_MA),
                        dC_PR = C_PR - lag(C_PR),
                        dERC_PR = ERC_PR - lag(ERC_PR)) %>% 
                 ungroup


```



# Amortization methods and periods

## 100% Initial Funding

```{r, echo = FALSE, cache = F , eval = TRUE, fig.width=20, fig.height=4}

prefix <- "A1F100_"

A1F100_FR     <- draw_quantiles(paste0(prefix, c(0:3, "3c") ), "FR",    ylim = c(0, 250))    
A1F100_C_PR   <- draw_quantiles(paste0(prefix, c(0:3, "3c")), "C_PR",   ylim = c(-2, 35))
A1F100_ERC_PR <- draw_quantiles(paste0(prefix, c(0:3, "3c")), "ERC_PR", ylim = c(-2, 35))

A1F100_FR$plot
A1F100_C_PR$plot
A1F100_ERC_PR$plot

A1F100_FR$df %>% glimpse()
A1F100_C_PR$df
A1F100_ERC_PR$plot

# Amortization period with cp payment
draw_quantiles(paste0(prefix, c(0, 1, "1cp",2,3, "3c") ), "FR",    ylim = c(0, 250))$plot  
draw_quantiles(paste0(prefix, c(0, 1, "1cp",2,3, "3c")), "C_PR",   ylim = c(-2, 35))$plot

# Amortization period with cd payment
draw_quantiles(paste0(prefix, c(0, "1", "2") ), "FR",    ylim = c(0, 250))$plot  
draw_quantiles(paste0(prefix, c(0, "1", "2")), "C_PR",   ylim = c(-2, 35))$plot


cp <- sapply(1:30, function(x) gaip(100, 0.075, x, 0.03))
cd <- sapply(1:30, function(x) pmt(100, 0.075, x))

cd 
cp

data.frame(cd = cd, cp = cp, year = 1:length(cd)) %>% gather(method, payment, -year) %>% 
  ggplot(aes(year, payment, color = method)) + geom_point() + geom_line() + 
  ggtitle("1st-year payment under differnt methods and amortization period (pricipal = 100)")


```


## 75% Initial Funding

```{r, echo = FALSE, cache = F , eval = TRUE, fig.width=20, fig.height=4}

prefix <- "A1F075_"

draw_quantiles(c(paste0(prefix, 0), paste0(prefix, 1:3,"c")), "FR", ylim = c(0, 250))$plot %>% print
draw_quantiles(c(paste0(prefix, 0), paste0(prefix, 1:3,"c")), "C_PR", ylim = c(-2, 35))$plot %>% print
draw_quantiles(c(paste0(prefix, 0), paste0(prefix, 1:3,"c")), "ERC_PR", ylim = c(-2, 35))$plot %>% print


draw_quantiles(paste0(prefix, c(0:3, "3c") ), "FR", ylim = c(0, 250))$plot %>% print
draw_quantiles(paste0(prefix, c(0:3, "3c")), "C_PR", ylim = c(-2, 35))$plot %>% print
draw_quantiles(paste0(prefix, c(0:3, "3c")), "ERC_PR", ylim = c(-2, 35))$plot %>% print


# Amortization period with cp payment
draw_quantiles(paste0(prefix, c(0, 1, "1cp",2,3,6, "3c")) , "FR_MA",    ylim = c(0, 250))$plot  
draw_quantiles(paste0(prefix, c(0, 1, "1cp",2,3,6, "3c")) , "C_PR",   ylim = c(-2, 35))$plot

draw_quantiles("A1F075_6" , "FR_MA", ylim = c(0, 250))$df %>% filter(Quantile == "50%")



```




# Asset Smoothing 

## 100% Initial Funding: Long term effect

```{r, echo = FALSE, cache = F , eval = TRUE, fig.width=20, fig.height=4}

prefix <- "A1F100_"

# 5-year and 10-year smoothing compared with 30-year open cp amortization  
draw_quantiles(paste0(prefix, c(3, 6, 7)), "FR", ylim = c(0, 250))$plot %>% print
draw_quantiles(paste0(prefix, c(3, 6, 7)), "FR_MA", ylim = c(0, 250))$plot %>% print
draw_quantiles(paste0(prefix, c(3, 6, 7)), "C_PR", ylim = c(-2, 35))$plot %>% print
draw_quantiles(paste0(prefix, c(3, 6, 7)), "ERC_PR", ylim = c(-2, 35))$plot %>% print

# 5-year and 10-year smoothing compared with 30-year open cd amortization  
draw_quantiles(paste0(prefix, c(2, 8, 9)), "FR", ylim = c(0, 250))$plot %>% print
draw_quantiles(paste0(prefix, c(2, 8, 9)), "FR_MA", ylim = c(0, 250))$plot %>% print
draw_quantiles(paste0(prefix, c(2, 8, 9)), "C_PR", ylim = c(-2, 35))$plot %>% print
draw_quantiles(paste0(prefix, c(2, 8, 9)), "ERC_PR", ylim = c(-2, 35))$plot %>% print

# 5-year and 10-year smoothing compared with no amortization 
draw_quantiles(paste0(prefix, c(0, 4, 5)), "FR", ylim = c(0, 250))$plot %>% print
draw_quantiles(paste0(prefix, c(0, 4, 5)), "C_PR", ylim = c(-2, 35))$plot %>% print
draw_quantiles(paste0(prefix, c(0, 4, 5)), "ERC_PR", ylim = c(-2, 35))$plot %>% print

```
# Calculate Measures of volatility in FR and contribution

```{r}
# 30-year open cp, no amortization 

prefix <- "A1F100_"

get_vol_MA <- function(runName, year.max, data = results_all){
         df <-  data %>% 
                filter(runname == runName, year <= year.max) %>%
                group_by(sim) %>% 
                summarize(avg_dFR     = mean(abs(dFR), na.rm = TRUE),
                          avg_dFR_MA  = mean(abs(dFR_MA), na.rm = TRUE),
                          avg_dC_PR   = mean(abs(dC_PR), na.rm = TRUE),
                          avg_dERC_PR = mean(abs(dERC_PR), na.rm = TRUE)) %>% 
                summarize(m_avg_dFR     = median(avg_dFR),
                          m_avg_dFR_MA  = median(avg_dFR_MA),
                          m_avg_dC_PR   = median(avg_dC_PR),
                          m_avg_dERC_PR = median(avg_dERC_PR)) %>% 
                mutate(runname = runName) %>% 
                select(runname, everything())
}

get_vol_MM <- function(runName, year.max, data = results_all){
         df <-  data %>% 
                filter(runname == runName, year <= year.max) %>%
                group_by(sim) %>% 
                summarize(avg_dFR     = median(abs(dFR), na.rm = TRUE),
                          avg_dFR_MA  = median(abs(dFR_MA), na.rm = TRUE),
                          avg_dC_PR   = median(abs(dC_PR), na.rm = TRUE),
                          avg_dERC_PR = median(abs(dERC_PR), na.rm = TRUE)) %>% 
                summarize(m_avg_dFR     = median(avg_dFR),
                          m_avg_dFR_MA  = median(avg_dFR_MA),
                          m_avg_dC_PR   = median(avg_dC_PR),
                          m_avg_dERC_PR = median(avg_dERC_PR)) %>% 
                mutate(runname = runName) %>% 
                select(runname, everything())
}


# 20 years is a more practical timeframe from the perspective of policymaking. Hence a measureo of volatility in 20 years 
# rather than in the entire 80-year simulation period is more relevant to plan sponsors and policymakers. 

sum_vol100_MM20 <- adply(paste0("A1F100_", c(0, 1:3, paste0(1:3,"c"),4, 5, 6, 7)), 1, get_vol_MM, year.max = 20) %>% select(-X1)
sum_vol075_MA20 <- adply(paste0("A1F075_", c(0, 1:3, paste0(1:3,"c"),4, 5, 6, 7)), 1, get_vol_MA, year.max = 20) %>% select(-X1)
sum_vol100_MA20 <- adply(paste0("A1F100_", c(0, 1:3, paste0(1:3,"c"),4, 5, 6, 7)), 1, get_vol_MA, year.max = 20) %>% select(-X1)

sum_vol100_MM40 <- adply(paste0("A1F100_", c(0, 1:3, paste0(1:3,"c"),4, 5, 6, 7)), 1, get_vol_MM, year.max = 40) %>% select(-X1)
sum_vol100_MA40 <- adply(paste0("A1F100_", c(0, 1:3, paste0(1:3,"c"),4, 5, 6, 7)), 1, get_vol_MA, year.max = 40) %>% select(-X1)

sum_vol100_MM80 <- adply(paste0("A1F100_", c(0, 1:3, paste0(1:3,"c"),4, 5, 6, 7)), 1, get_vol_MM, year.max = 80) %>% select(-X1)
sum_vol100_MA80 <- adply(paste0("A1F100_", c(0, 1:3, paste0(1:3,"c"),4, 5, 6, 7)), 1, get_vol_MA, year.max = 80) %>% select(-X1)

sum_vol100_MM20
sum_vol100_MA20

sum_vol100_MM40
sum_vol100_MA40

sum_vol100_MM80
sum_vol100_MA80

# 100% and 75% initial funded ratio
sum_vol100_MA20
sum_vol075_MA20

# Thoughts:

# The distribution of abs values are quite skewed and the difference between mean and median for all variables is big.

# The current "no smoothing" policy may not be a good benchmark for comparison of long-term volatility in cont rates. Because contribution rate becomes 0 after a few decades in a substantial number of simulations. So the variation this mostly due to the wild swings during early years in the simulation. But there are variation in cont. rate for other policies. Therefore it may not be fair to compare their vaiation. The "no smoothing" policy can be a good benchmark if there is no non-neg restrictions on ADC and contribution, so contribution rate can swing freely. 

# One problem with the M-M measure is that the measure becomes 0 if we look at more than 20 years, because there are lots of 0 contribution by by then. The M-A measure does not have this problem. 

# It seems ok for now to use M-A measure. But we may want to think about other measure b/c we are trying to measure very skewed distributions.

# Another possible measure is the % of years in which contribution rate is greater than a certain value. The question is what value to use. 

# We may want to devise an index based on paired comparison(compare results from different policies for the same single sim). This way we may see the trade-off between vol. in FR and vol. in cont. rate.  v


## Check the distribution of annual change

var_list <- c("runname", "sim", "year","FR", "dFR","FR_MA", "dFR_MA", "dC_PR", "dERC_PR", "i.r")

df_avg <- results_all %>% 
          filter(runname == "A1F100_6") %>%
          select(one_of(var_list))

df_avg141 <- df_avg %>% filter(sim == 141)
mean(df_avg141$dFR_MA, na.rm = TRUE)  # 47%
get_geoReturn(df_avg141$i.r) # geometric mean 9.4%
var(df_avg141$i.r)^0.5 # variance 12.7%


df_avg$dFR_MA %>% abs %>%  summary
df_avg$dFR %>% abs %>% summary
df_avg$dC_PR %>% abs %>% summary
df_avg$dERC_PR %>% abs %>%  summary



df_avg2 <- df_avg %>% group_by(sim) %>%  
                    summarize(avg_dFR = mean(abs(dFR), na.rm = TRUE),
                          avg_dFR_MA  = mean(abs(dFR_MA), na.rm = TRUE),
                          avg_dC_PR   = mean(abs(dC_PR), na.rm = TRUE),
                          avg_dERC_PR = mean(abs(dERC_PR), na.rm = TRUE))

df_avg2$avg_dFR_MA %>% hist
df_avg2$avg_dFR %>% hist
df_avg2$avg_dC_PR %>% hist
df_avg2$avg_dERC_PR %>% hist

df_avg2$avg_dFR_MA %>% summary
df_avg2$avg_dFR %>% summary
df_avg2$avg_dC_PR %>% summary
df_avg2$avg_dERC_PR %>% summary

# distribution of contribution rate is quite irregular, is this normal or due to a too small number of sims?







```

## 100% Initial Funding: Long term effect: Single runs with high ending FR

```{r, echo = FALSE, cache = F , eval = TRUE, fig.width=20, fig.height=4}

prefix <- "A1F100_"

## Compare funding policy under the same simulation
runnames <- paste0("A1F100_", c("3", "6", "7"))


results2 <-  results_all %>% 
             select(runname, year, sim, FR, C_PR) %>% 
             filter(year == 80, runname %in% runnames)
results2 %>% filter(FR > 120, FR < 130)

# high ending FR: 
sims <- c(36, 216, 232)
# low ending FR:  c(249, 435,525)

singleRuns <-  results_all %>% select(runname, year, sim, FR, FR_MA, C_PR, ERC_PR, i.r) %>% 
               filter(runname %in% runnames) %>% 
               filter(sim %in% sims) %>% 
               group_by(runname, sim) %>% 
               mutate(rollingReturn = 100 * rollapply(i.r, 10, get_geoReturn, align = "right", fill = NA)) %>% 
               gather(variable, value, -runname, -year, - sim) 
               

# 10-year rolling geometric return
singleRuns %>% filter(variable == "rollingReturn", runname == runnames[1]) %>% 
               ggplot(aes(x = year, y = value)) + theme_bw() + 
               facet_grid(. ~ sim) + # coord_cartesian(ylim = c(-5,150)) +
               geom_line() + geom_point() + 
               labs(y = "10-Year Rolling Average Return (%)", title = "10-year Rolling Geometric Average Return under Selected Runs with High Ending Funded Ratio")

# %>%  ggsave(filename = "IO_Prelim/R3_Rolling.png", width = 8, height = 3, dpi = 400)


# FR in single runs
singleRuns %>% filter(variable == "FR_MA", runname %in% runnames) %>% 
               ggplot(aes(x = year, y = value, color = runname)) + theme_bw() + 
               facet_grid(. ~ sim) + # coord_cartesian(ylim = c(-5,150)) +
               geom_line() + geom_point() + 
               labs(y = "Funded Ratio", title = "Funded Ratio in Selected Single Runs with High Ending Funded Ratio") + 
               scale_color_discrete(labels = c("No Smoothing", "5-year Smoothing", "10-year Smoothing")) +
               theme(legend.position="bottom", legend.margin = unit(-0.5, "cm"), legend.title=element_blank())

singleRuns %>% filter(variable == "C_PR", runname %in% runnames) %>% 
               ggplot(aes(x = year, y = value, color = runname)) + theme_bw() + 
               facet_grid(. ~ sim) + # coord_cartesian(ylim = c(-5,150)) +
               geom_line() + geom_point() + 
               labs(y = "Contribution Rate", title = "Contribution Rate in Selected Single Runs with High Ending Funded Ratio") + 
               scale_color_discrete(labels = c("No Smoothing", "5-year Smoothing", "10-year Smoothing")) +
               theme(legend.position="bottom", legend.margin = unit(-0.5, "cm"), legend.title=element_blank())

```

## 100% Initial Funding: Long term effect: Single runs with low ending FR

```{r, echo = FALSE, cache = F , eval = TRUE, fig.width=20, fig.height=4}

prefix <- "A1F100_"

## Compare funding policy under the same simulation
runnames <- paste0("A1F100_", c("3", "6", "7"))


results2 <-  results_all %>% 
             select(runname, year, sim, FR, C_PR) %>% 
             filter(year == 80, runname %in% runnames)
results2 %>% filter(FR > 120, FR < 130)

# high ending FR: c(36, 216, 232)
# low ending FR:  
sims <- c(249, 435,525)

singleRuns <-  results_all %>% select(runname, year, sim, FR, FR_MA, C_PR, ERC_PR, i.r) %>% 
               filter(runname %in% runnames) %>% 
               filter(sim %in% sims) %>% 
               group_by(runname, sim) %>% 
               mutate(rollingReturn = 100 * rollapply(i.r, 10, get_geoReturn, align = "right", fill = NA)) %>% 
               gather(variable, value, -runname, -year, - sim) 
               

# 10-year rolling geometric return
singleRuns %>% filter(variable == "rollingReturn", runname == runnames[1]) %>% 
               ggplot(aes(x = year, y = value)) + theme_bw() + 
               facet_grid(. ~ sim) + # coord_cartesian(ylim = c(-5,150)) +
               geom_line() + geom_point() + 
               labs(y = "10-Year Rolling Average Return (%)", title = "10-year Rolling Geometric Average Return under Selected Runs with High Ending Funded Ratio")

# %>%  ggsave(filename = "IO_Prelim/R3_Rolling.png", width = 8, height = 3, dpi = 400)


# FR in single runs
singleRuns %>% filter(variable == "FR_MA", runname %in% runnames) %>% 
               ggplot(aes(x = year, y = value, color = runname)) + theme_bw() + 
               facet_grid(. ~ sim) + # coord_cartesian(ylim = c(-5,150)) +
               geom_line() + geom_point() + 
               labs(y = "Funded Ratio", title = "Funded Ratio in Selected Single Runs") + 
               scale_color_discrete(labels = c("No Asset Smoothing", "5-year Asset Smoothing", "10-year Asset Smoothing")) +
               theme(legend.position="bottom", legend.margin = unit(-0.5, "cm"), legend.title=element_blank())

singleRuns %>% filter(variable == "C_PR", runname %in% runnames) %>% 
               ggplot(aes(x = year, y = value, color = runname)) + theme_bw() + 
               facet_grid(. ~ sim) + # coord_cartesian(ylim = c(-5,150)) +
               geom_line() + geom_point() + 
               labs(y = "Contribution Rate", title = "Contribution Rate in Selected Single Runs") + 
               scale_color_discrete(labels = c("No Asset Smoothing", "5-year Asset Smoothing", "10-year Asset Smoothing")) +
               theme(legend.position="bottom", legend.margin = unit(-0.5, "cm"), legend.title=element_blank())

```


# Comparison between no smoothing and smoothing 

```{r}

# Compare no smoothing to smoothing 
fn <- function(x) 100 * sum(x)/length(x)

df <- results_all %>% filter(runname %in% runnames) %>% select(runname, sim, year, FR, FR_MA, C_PR, ERC_PR) %>% 
                gather(var, value, -runname, -sim, -year) %>% 
                mutate(var = paste0(var, substr(runname, 8, 8) )) %>% 
                select(sim,year, var, value)%>% 
                spread(var, value) %>% 
                mutate(FR_L5  =  FR6 <  FR3,
                       FR_L10 =  FR7 <  FR3,
                       FR_MA_L5  =  FR_MA6 <  FR_MA3,
                       FR_MA_L10 =  FR_MA7 <  FR_MA3,
                       C_L5  =   C_PR6 > C_PR3,
                       C_L10 =   C_PR7 > C_PR3,
                       ERC_L5  = ERC_PR6 > ERC_PR3,
                       ERC_L10 = ERC_PR7 > ERC_PR3
                       ) %>% 
       group_by(year) %>% 
       summarize(FR_L5  = fn(FR_L5),
                 FR_L10 = fn(FR_L10),
                 FR_MA_L5  = fn(FR_MA_L5),
                 FR_MA_L10 = fn(FR_MA_L10),
                 C_L5  =  fn(C_L5),
                 C_L10 =  fn(C_L10),
                 ERC_L5  =fn(ERC_L5),
                 ERC_L10 =fn(ERC_L10))



df2 <- df %>% gather(var, value, -year) %>% 
              mutate(type = ifelse(var %in% c("FR_L5", "FR_L10"), "Funded Ratio Based on Actuarial Value", NA),
                     type = ifelse(var %in% c("FR_MA_L5", "FR_MA_L10"), "Funded Ratio Based on Market Value", type),
                     type = ifelse(var %in% c("C_L5", "C_L10"), "Total Contribution Rate", type),
                     type = ifelse(var %in% c("ERC_L5", "ERC_L10"), "Employer Contribution Rate", type),
                     
                     sth  = ifelse(var %in% c("FR_L5", "FR_MA_L5", "C_L5", "ERC_L5"), "5-year Smoothing", NA),
                     sth  = ifelse(var %in% c("FR_L10", "FR_MA_L10", "C_L10", "ERC_L10"), "10-year Smoothing", sth),
              
                     type = factor(type, levels = c("Funded Ratio Based on Actuarial Value",
                                                    "Funded Ratio Based on Market Value",
                                                    "Total Contribution Rate",
                                                    "Employer Contribution Rate")),
                     sth = factor(sth, levels = c("5-year Smoothing", "10-year Smoothing"))
                     )




df2 %>% filter(substr(type, 1, 1) == "F", year !=1) %>% 
       ggplot(aes(x = year, y = value, color = sth)) + theme_bw() + facet_grid(. ~ type) + 
       geom_line() + geom_point() + geom_hline(yintercept = 50, linetype = 2) + 
       coord_cartesian(ylim = c(-5, 105))+
       scale_color_manual(values = c("green3", "blue"), labels = c("5-year Smoothing", "10-year Smoothing")) +
       theme(legend.position="bottom", legend.margin = unit(-0.5, "cm"), legend.title=element_blank()) + 
       labs(y = "%", title = "Percentage of Simulations in which Asset Smoothing Methods Lead to Lower Funded Ratio")


df2 %>% filter(substr(type, 1, 1) != "F", year !=1) %>% 
       ggplot(aes(x = year, y = value, color = sth)) + theme_bw() + facet_grid(. ~ type) + 
       geom_line() + geom_point() + geom_hline(yintercept = 50, linetype = 2) + 
       coord_cartesian(ylim = c(-5, 105))+
       scale_color_manual(values = c("green3", "blue"), labels = c("5-year Smoothing", "10-year Smoothing")) +
       theme(legend.position="bottom", legend.margin = unit(-0.5, "cm"), legend.title=element_blank()) + 
       labs(y = "%", title = "Percentage of Simulations in which Asset Smoothing Methods Lead to Higher Contribution Rate")



```



## -25%  Initial Funding shock

```{r, echo = FALSE, cache = F , eval = TRUE, fig.width=20, fig.height=4}

prefix <- "A1F075_"

# 15-year zoom in
draw_quantiles(paste0(prefix, c("0a", "4a", "5a")), "FR", ylim = c(0, 250),     year.max = 15)$plot %>% print
draw_quantiles(paste0(prefix, c("0a", "4a", "5a")), "FR_MA", ylim = c(0, 250),  year.max = 15)$plot %>% print
draw_quantiles(paste0(prefix, c("0a", "4a", "5a")), "C_PR", ylim = c(-2, 35),   year.max = 15)$plot %>% print
draw_quantiles(paste0(prefix, c("0a", "4a", "5a")), "ERC_PR", ylim = c(-2, 35), year.max = 15)$plot %>% print

draw_quantiles(paste0(prefix, c("3a", "6a", "7a")), "FR", ylim = c(0, 125),     year.max = 20)$plot %>% print
draw_quantiles(paste0(prefix, c("3a", "6a", "7a")), "FR_MA", ylim = c(0, 125),  year.max = 20)$plot %>% print
draw_quantiles(paste0(prefix, c("3a", "6a", "7a")), "C_PR", ylim = c(-2, 20),   year.max = 20)$plot %>% print
draw_quantiles(paste0(prefix, c("3a", "6a", "7a")), "ERC_PR", ylim = c(-2, 20), year.max = 20)$plot %>% print

# 80-year view
draw_quantiles(paste0(prefix, c("0a", "4a", "5a")), "FR", ylim = c(0, 250),     year.max = 80)$plot %>% print
draw_quantiles(paste0(prefix, c("0a", "4a", "5a")), "FR_MA", ylim = c(0, 250),  year.max = 80)$plot %>% print
draw_quantiles(paste0(prefix, c("0a", "4a", "5a")), "C_PR", ylim = c(-2, 35),   year.max = 80)$plot %>% print
draw_quantiles(paste0(prefix, c("0a", "4a", "5a")), "ERC_PR", ylim = c(-2, 35), year.max = 80)$plot %>% print

draw_quantiles(paste0(prefix, c("3a", "6a", "7a")), "FR", ylim = c(0, 250),     year.max = 80)$plot %>% print
draw_quantiles(paste0(prefix, c("3a", "6a", "7a")), "FR_MA", ylim = c(0, 250),  year.max = 80)$plot %>% print
draw_quantiles(paste0(prefix, c("3a", "6a", "7a")), "C_PR", ylim = c(-2, 35),   year.max = 80)$plot %>% print
draw_quantiles(paste0(prefix, c("3a", "6a", "7a")), "ERC_PR", ylim = c(-2, 35), year.max = 80)$plot %>% print

# draw_quantiles(paste0(prefix, c("3a", "6a", "7a")), "FR", ylim = c(0, 250),     year.max = 80)$df

# Look at single runs



## Compare funding policy under the same simulation

runnames <- paste0(prefix, c("0a", "4a", "5a"))
# runnames <- paste0(prefix, c("3a", "6a", "7a"))
# runnames <- paste0("A1F100-", c("3", "6", "7"))


results2 <-  results_all %>% 
             select(runname, year, sim, FR, C_PR) %>% 
             filter(year == 80, runname %in% runnames)
results2 %>% filter(FR > 150, FR < 155)



singleRuns <-  results_all %>% select(runname, year, sim, FR, FR_MA, C_PR, ERC_PR, i.r) %>% 
               filter(runname %in% runnames) %>% 
               filter(sim %in% c(36, 289, 357)) %>% 
               group_by(runname, sim) %>% 
               mutate(rollingReturn = 100 * rollapply(i.r, 10, get_geoReturn, align = "right", fill = NA)) %>% 
               gather(variable, value, -runname, -year, - sim) 
               
# c(25, 249, 309)              
# c(249, 435,525)

# 5-year rolling geometric return
singleRuns %>% filter(variable == "rollingReturn", runname == runnames[1]) %>% 
               ggplot(aes(x = year, y = value)) + theme_bw() + 
               facet_grid(. ~ sim) + # coord_cartesian(ylim = c(-5,150)) +
               geom_line() + geom_point() + 
               labs(y = "10-Year Rolling Average Return (%)", title = "10-year Rolling Geometric Average Return under Selected Runs")

# %>%  ggsave(filename = "IO_Prelim/R3_Rolling.png", width = 8, height = 3, dpi = 400)


# FR in single runs
singleRuns %>% filter(variable == "FR_MA", runname %in% runnames) %>% 
               ggplot(aes(x = year, y = value, color = runname)) + theme_bw() + 
               facet_grid(. ~ sim) + # coord_cartesian(ylim = c(-5,150)) +
               geom_line() + geom_point() + 
               labs(y = "Funded Ratio", title = "Funded Ratio in Selected Single Runs")

singleRuns %>% filter(variable == "C_PR", runname %in% runnames) %>% 
               ggplot(aes(x = year, y = value, color = runname)) + theme_bw() + 
               facet_grid(. ~ sim) + # coord_cartesian(ylim = c(-5,150)) +
               geom_line() + geom_point() + 
               labs(y = "Contribution Rate", title = "Contribution Rate in Selected Single Runs")


```


## 75% Initial Funding

```{r, echo = FALSE, cache = F , eval = TRUE, fig.width=20, fig.height=4}

prefix <- "A1F075-"

draw_quantiles(paste0(prefix, c(0, 4, 5)), "FR", ylim = c(0, 250))$plot %>% print
draw_quantiles(paste0(prefix, c(0, 4, 5)), "C_PR", ylim = c(-2, 35))$plot %>% print
draw_quantiles(paste0(prefix, c(0, 4, 5)), "ERC_PR", ylim = c(-2, 35))$plot %>% print


draw_quantiles(paste0(prefix, c(3, 6, 7)), "FR", ylim = c(0, 250))$plot %>% print
draw_quantiles(paste0(prefix, c(3, 6, 7)), "C_PR", ylim = c(-2, 35))$plot %>% print
draw_quantiles(paste0(prefix, c(3, 6, 7)), "ERC_PR", ylim = c(-2, 35))$plot %>% print

```


# Discount rate and BRP assumptions

## Forward looking vs Backward looking discount (BRP assumptions)

```{r, echo = FALSE, cache = F , eval = TRUE, fig.width=20, fig.height=4}

prefix <- "B2F100_"
draw_quantiles(paste0(prefix, c(0, 1, 2, 3)), "FR", ylim = c(0, 250))$plot   %>% print
draw_quantiles(paste0(prefix, c(0, 1, 2, 3)), "C_PR", ylim = c(-2, 35))$plot  %>% print
draw_quantiles(paste0(prefix, c(0, 1, 2, 3)), "ERC_PR", ylim = c(-2, 35))$plot  %>% print


prefix <- "B2F075_"
draw_quantiles(paste0(prefix, c(0, 1, 2, 3)), "FR", ylim = c(0, 250))$plot  %>% print
draw_quantiles(paste0(prefix, c(0, 1, 2, 3)), "C_PR", ylim = c(-2, 35))$plot  %>% print
draw_quantiles(paste0(prefix, c(0, 1, 2, 3)), "ERC_PR", ylim = c(-2, 35))$plot  %>% print



# Intial Liability in 0 and 1

results_all %>% filter(runname %in% paste0("B2F100_", c(0, 1)), year == 1, sim %in% 1:2) %>% 
                select(runname, sim, year, AL, AA, MA)
#    runname sim year        AL        AA        MA
# 1 B2F100_0   1    1 143423401 143423401 143423401


results_all %>% filter(runname %in% paste0("B2F075_", c(0, 1)), year == 1, sim %in% 1:2) %>% 
                select(runname, sim, year, AL, AA, MA)
#    runname sim year        AL        AA        MA
# 1 B2F075_0   1    1 143423401 107567551 107567551


results_all %>% filter(runname %in% paste0("B2F075_2a"), year == 1, sim %in% 1:2) %>% 
                select(runname, sim, year, AL, AA, MA, FR,FR_MA)


# now BRP plans with DC = 6.4% have the same initial asset as plans with DC = 7.5%
prefix <- "B2F100_"
draw_quantiles(paste0(prefix, c(0, 1, "2a", "3a")), "FR", ylim = c(0, 250))$plot   %>% print
draw_quantiles(paste0(prefix, c(0, 1, "2a", "3a")), "C_PR", ylim = c(-2, 35))$plot  %>% print

prefix <- "B2F075_"
draw_quantiles(paste0(prefix, c(0, 1, "2a", "3a")), "FR", ylim = c(0, 250))$plot   %>% print
draw_quantiles(paste0(prefix, c(0, 1, "2a", "3a")), "C_PR", ylim = c(-2, 35))$plot  %>% print

```


## Geometric mean vs Arithmetic mean

```{r, echo = FALSE, cache = F , eval = TRUE, fig.width=20, fig.height=4}

prefix <- "B1F100_"
draw_quantiles(paste0(prefix, c(0, 1)), "FR", ylim = c(0, 250))$plot %>% print
draw_quantiles(paste0(prefix, c(0, 1)), "C_PR", ylim = c(-2, 35))$plot %>% print
draw_quantiles(paste0(prefix, c(0, 1)), "ERC_PR", ylim = c(-2, 35))$plot %>% print


prefix <- "B1F075_"
draw_quantiles(paste0(prefix, c(0, 1)), "FR", ylim = c(0, 250))$plot %>% print
draw_quantiles(paste0(prefix, c(0, 1)), "C_PR", ylim = c(-2, 35))$plot %>% print
draw_quantiles(paste0(prefix, c(0, 1)), "ERC_PR", ylim = c(-2, 35))$plot %>% print

```








